---
title: "James Brian Elsner"
params:
   address: Tallahassee, Florida and Sofia, Bulgaria
   email: jelsner@fsu.edu
---

<!--html_preserve-->
<style type="text/css">
ul.CV {
list-style-type: none;
}
</style>
<!--/html_preserve-->

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(RefManageR)
```

<ul class="CV">

<li><i class="fa fa-home" aria-hidden="true"></i> `r paste(" ", params$address)`</li>

<li><i class="fa fa-envelope-o" aria-hidden="true"></i> `r paste(" ", params$email)`</li>

<li><i class="fa fa-clock-o" aria-hidden="true"></i> Last Updated: `r paste(" ", format(Sys.Date(), "%B %d, %Y"))`</li>

</ul>

------------------------------------------------------------------------

# Education

-   1988 - 1990: PostDoc - University of Wisconsin-Milwaukee
-   1984 - 1988: PhD in Geosciences - University of Wisconsin-Milwaukee
-   1981 - 1984: MSc in Meteorology - University of Wisconsin-Milwaukee
-   1977 - 1981: BSc in Meteorology - University of Wisconsin-Milwaukee

------------------------------------------------------------------------

# Professional Experience

-   2024 - present
    -   Professor Emeritus, Florida State University
-   2008 - 2023
    -   Earl B. and Sophia H. Shaw Professor, Department of Geography, Florida State University
-   2012 - 2023
    -   Faculty Associate, Geophysical Fluid Dynamics Institute, Florida State University
-   2015 - 2021
    -   Chair, Department of Geography, Florida State University
-   2001 - 2016
    -   President of *Climatek Inc.*
-   2001 - 2008
    -   Professor, Department of Geography, Florida State University
-   1998 - 2001
    -   Associate Professor, Department of Geography, Florida State University
-   1995 - 1998
    -   Associate Professor, Department of Meteorology, Florida State University
-   1990 - 1995
    -   Assistant Professor, Department of Meteorology, Florida State University

------------------------------------------------------------------------

# PhD Students Graduated

-   Matthew M. Carter, *A quantitative precipitation forecast experiment for Puerto Rico*, 1999
-   Brian H. Bossak, *Early nineteenth-century United States hurricanes: A GIS tool and climate analysis*, 2003
-   Jeffrey James Dickey, *Improved flood prediction from basin elevation distribution*, 2006
-   Todd H. Albert, *Assessing glacier mass balances from small tropical glaciers to the large ice sheet of Greenland*, 2007
-   Emily A. Fogarty, *Network analysis of hurricanes affecting the United States*, 2009
-   Kelsey Nicole Scheitlin, *Construction and application of a spatial hurricane climatology*, 2010
-   Heather A. Gamper (co), *Effects of scale insects on forest dynamics in tropical montane oak forests of Veracruz, Mexico*, 2012
-   Jill Trepanier, *Quantifying extreme hurricane risk in the North Atlantic and Gulf of Mexico*, 2012
-   Robert Edward Hodges, *Understanding and predicting the regional sun-hurricane count relationship*, 2013
-   Nam-Young Kang, *Global warming and tropical cyclone climate in the western North Pacific*, 2014
-   Sarah Strazzo, *Assessing the ability of climate models to simulate the observed sensitivity of tropical cyclone intensity to sea surface temperature*, 2015
-   Erik Fraza, *Spatial analyses of climatological effects on hurricane intensification rates*, 2016
-   Peter Wood (co)
-   Holly M. Widen, *New methods in tornado risk and vulnerability assessments*, 2016
-   John M. Humphreys, *Traits, Species, and Communities: Integrative Bayesian Approaches to Ecological Biogeography across Geographic, Environmental, Phylogenetic, and Morphological Space*, 2018
-   Tyler Fricker, *A Geography of Tornado Casualties in the United States*, 2019
-   Gregory Burris (co), *Between proxy and instrument: Reconstructing past weather using qualitative human observations in the absence of instrumental and prox records: A case study from Shirley Plantation, Virginia*, 2021
-   Zoe Schroder, *Tornado Outbreak Climatology in the United States (1995–2020): Definitions, Descriptions, and Statistical Analyses*, 2021
-   Efraim Roxas (co), *Critical Vulnerability and Community Care Towards a Resilience from Below*, 2023

# MS Students Graduated

-   Vincint Robert Tino, *A validation of the industrial source complex (ISC2) dispersion model in the Kuwaiti oil fire situation*, 1992
-   Jason C. Hess, *Improving seasonal predictions of hurricane activity for the Atlantic basin*, 1994
-   Matthew M. Carter, *Convective rainfall regions in Puerto Rico*, 1995
-   Todd B. Kimberlain, *Baroclinically-initiated hurricanes of the North Atlantic basin*, 1996
-   Kwan Kong, *Landfall and post-landfall structure of Hurricane Danny and the possibility of retrieving vertical velocity profiles from rawinsonde soundings*, 1999
-   David Whitehead, *An evaluation of coastal county hurricane vulnerability*, 1999
-   Wei tan Pan (co),
-   Bethany Kocher, *Tropical cyclones and the North Atlantic oscillation*, 2000
-   Marc D. Cooper, *The association of human activities with land degradation in the Republic of Botswana*, 2000
-   Ethan J. Gibney, *An assessment of potential for economic loss to residential property in United States coastal counites [i.e., counties] from tropical cyclones using a geographical information system*, 2002
-   Emily A. Fogarty, *Variations in typhoon landfalls over China*, 2004
-   Jill Malmstadt, *Pre-landfall intensity as predictor of economic loss from Florida hurricanes, 1900-2007*, 2009
-   Robert Edward Hodges, *Evidence for a solar influence on U.S.-affecting hurricanes*, 2009
-   Ona Marie Strikas, *Modeling the spatial differentiation in cloud-to-ground lightning: A case study in Atlanta, Georgia, USA*, 2023
-   Laura E. Michaels, *Spatial and temporal characteristics of the population bias in U.S. tornado reports*, 2013
-   Tyler Fricker, *Estimating kinetic energy of U.S. tornadoes*, 2015
-   Emily Ryan, *Florida's Tornado Climatology: Occurrence Rates, Casualties, and Property Losses*, 2018
-   Zachery Taylor Law, *Wildfires in the Apalachicola National Forest, USA from 1992–2018: Relationships to Soil Dryness and Lightning*, 2022

# Grant Totals

-   Risk Prediction Initiative \$355,475
-   National Science Foundation \$1,306,348
-   National Oceanic and Atmospheric Administration \$96,000
-   Florida State University \$122,500

# Awards

-   Late Career Research Award College of Social Sciences and Public Policy, 2022, FSU.
-   Earl & Sophia Shaw Endowed Chair in Geography, FSU.
-   University Graduate Mentor Award, 2019, FSU.
-   Gilbert F. White Distinguished Lecture Award, 2013, American Geophysical Union.
-   Teaching Incentive Program Award, 1996, FSU.
-   Outstanding Student Teacher Award, 1987, UWM.

# Academic Books

```{r echo=FALSE, results="asis",comment=FALSE}
file_books <- ReadBib("books.bib")
dates <- unlist(unique(file_books$year))[order(unlist(unique(file_books$year)),decreasing = TRUE)]

for (date in dates) {
  print(file_books[list(year=date)],
        .opts = list(style="markdown",bib.style ="authoryear" ,max.names = 10, dashed=FALSE)
        )
  cat("\n")
}
```

# Refereed Academic Journal Articles

```{r echo=FALSE, results="asis",comment=FALSE}
file_journals <- ReadBib("journals.bib")
dates <- unlist(unique(file_journals$year))[order(unlist(unique(file_journals$year)), decreasing = TRUE)]

for (date in dates) {
  cat(paste0("## ", date),"\n")
  print(file_journals[list(year=date)],
        .opts = list(style="markdown", bib.style ="authoryear", max.names = 10, dashed=FALSE)
        )
  cat("\n")
}
```
