---
title: "James B. Elsner"
params:
   address: Department of Geography, Florida State University
   email: jelsner@fsu.edu
---

<!--html_preserve-->
<style type="text/css">
ul.CV {
list-style-type: none;
}
</style>
<!--/html_preserve-->

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(RefManageR)
```

<ul class="CV">
<li><i class="fa fa-home" aria-hidden="true"></i>  `r paste(" ", params$address)`</li>
<li><i class="fa fa-envelope-o" aria-hidden="true"></i>  `r paste(" ", params$email)`</li>
<li><i class="fa fa-clock-o" aria-hidden="true"></i> Last Updated: `r paste(" ", format(Sys.Date(), "%B %d, %Y"))`</li>
</ul>

*************

# Education

* 1988 - 90: PostDoc - University of Wisconsin-Milwaukee
* 1984 - 88: PhD in Geosciences - University of Wisconsin-Milwaukee
* 1981 - 84: MSc in Meteorology - University of Wisconsin-Milwaukee
* 1977 - 81: BSc in Meteorology - University of Wisconsin-Milwaukee

*************

# Professional Experience
* 2008 - present
    + Earl B. and Sophia H. Shaw Professor, Department of Geography, Florida State University
* 2012 - present
    + Faculty Associate, Geophysical Fluid Dynamics Institute, Florida State University
* 2015 - 2021
    + Chair, Department of Geography, Florida State University
* 2001 - 2016
    + President of *Climatek Inc.*
* 2001 - 2008
    + Professor, Department of Geography, Florida State University
* 1998 - 2001
    + Associate Professor, Department of Geography, Florida State University
* 1995 - 1998
    + Associate Professor, Department of Meteorology, Florida State University
* 1990 - 1995
    + Assistant Professor, Department of Meteorology, Florida State University

*************

# Students Graduated

* PhD: Matthew Carter (Meteorology), Brian Bossak (Meteorology), Jeff Dickey (Geography), Todd Albert (Geography), Emily Fogarty (Geography), Kelsey Scheitlin (Geography), Heather Gamper (co) (Geography), Jill Trepanier (Geography), Robert Hodges (Geography), Nam-Young Kang (Geophysical Fluid Dynamics Institute),  Sarah Strazzo (Geography), Erik Fraza (Geography), Peter Wood (co) (Geography), Holly Widen (Geography), John Humphreys (Geography), Tyler Fricker (Geography), Gregory Burris (co) (Geography), Zoe Schroder (Geography)

* MS: Vincint Tino (Meteorology), Jason Hess (Meteorology), Todd Kimberlain (Meteorology), Matthew Carter (Meteorology), Kwan Kong (Meteorology), David Whitehead (Meteorology), Weitan Pan (co) (Engineering), Bethany Kocher (Meteorology), Marc Cooper (Geography), Ethan Gibney (Geography), Emily Fogarty (Geography), Jill Malmstadt (Geography), Robert Hodges (Geography), Ona Strikas (Geography), Laura Michaels (Geography), Tyler Fricker (Geography), Emily Ryan (Geography)

# Grant Totals

* Risk Prediction Initiative $355,475
* National Science Foundation $1,306,348 
* National Oceanic and Atmospheric Administration $96,000
* Florida State University $122,500

# Awards

* Late Career Research Award College of Social Sciences and Public Policy, 2022, FSU.
* Earl & Sophia Shaw Endowed Chair in Geography, FSU.
* University Graduate Mentor Award, 2019, FSU.
* Gilbert F. White Distinguished Lecture Award, 2013, American Geophysical Union.
* Teaching Incentive Program Award, 1996, FSU.
* Outstanding Student Teacher Award, 1987, UWM.

# Academic Books

```{r echo=FALSE, results="asis",comment=FALSE}
file_books <- ReadBib("books.bib")
dates <- unlist(unique(file_books$year))[order(unlist(unique(file_books$year)),decreasing = TRUE)]

for (date in dates) {
  print(file_books[list(year=date)],
        .opts = list(style="markdown",bib.style ="authoryear" ,max.names = 10, dashed=FALSE)
        )
  cat("\n")
}
```

# Refereed Academic Journal Articles

```{r echo=FALSE, results="asis",comment=FALSE}
file_journals <- ReadBib("journals.bib")
dates <- unlist(unique(file_journals$year))[order(unlist(unique(file_journals$year)), decreasing = TRUE)]

for (date in dates) {
  cat(paste0("## ", date),"\n")
  print(file_journals[list(year=date)],
        .opts = list(style="markdown", bib.style ="authoryear", max.names = 10, dashed=FALSE)
        )
  cat("\n")
}
```
