---
title: "James B. Elsner"
params:
   email: jelsner@fsu.edu
---

<!--html_preserve-->
<style type="text/css">
ul.CV {
list-style-type: none;
}
</style>
<!--/html_preserve-->

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(RefManageR)
```

<ul class="CV">
<li><i class="fa fa-home" aria-hidden="true"></i>  `r paste(" ", params$address)`</li>
<li><i class="fa fa-envelope-o" aria-hidden="true"></i>  `r paste(" ", params$email)`</li>
<li><i class="fa fa-clock-o" aria-hidden="true"></i> Last Updated: `r paste(" ", format(Sys.Date(), "%B %d, %Y"))`</li>
</ul>

*************

# Education

* 1988 - 1990: PostDoc - University of Wisconsin-Milwaukee
* 1984 - 1988: PhD in Geosciences - University of Wisconsin-Milwaukee
* 1981 - 1984: MSc in Meteorology - University of Wisconsin-Milwaukee
* 1977 - 1981: BSc in Meteorology - University of Wisconsin-Milwaukee

*************

# Professional Experience
* 2008 - 2023
    + Earl B. and Sophia H. Shaw Professor, Department of Geography, Florida State University
* 2012 - 2023
    + Faculty Associate, Geophysical Fluid Dynamics Institute, Florida State University
* 2015 - 2021
    + Chair, Department of Geography, Florida State University
* 2001 - 2016
    + President of *Climatek Inc.*
* 2001 - 2008
    + Professor, Department of Geography, Florida State University
* 1998 - 2001
    + Associate Professor, Department of Geography, Florida State University
* 1995 - 1998
    + Associate Professor, Department of Meteorology, Florida State University
* 1990 - 1995
    + Assistant Professor, Department of Meteorology, Florida State University

*************

# PhD Students Graduated

- Matthew M. Carter, _A quantitative precipitation forecast experiment for Puerto Rico_, 1999
- Brian H. Bossak, _Early nineteenth-century United States hurricanes: A GIS tool and climate analysis_, 2003
- Jeffrey James Dickey, _Improved flood prediction from basin elevation distribution_, 2006
- Todd H. Albert, _Assessing glacier mass balances from small tropical glaciers to the large ice sheet of Greenland_, 2007
- Emily A. Fogarty, _Network analysis of hurricanes affecting the United States_, 2009
- Kelsey Nicole Scheitlin, _Construction and application of a spatial hurricane climatology_, 2010
- Heather A. Gamper (co), _Effects of scale insects on forest dynamics in tropical montane oak forests of Veracruz, Mexico_, 2012
- Jill Trepanier, _Quantifying extreme hurricane risk in the North Atlantic and Gulf of Mexico_, 2012
- Robert Edward Hodges, _Understanding and predicting the regional sun-hurricane count relationship_, 2013
- Nam-Young Kang, _Global warming and tropical cyclone climate in the western North Pacific_, 2014
- Sarah Strazzo, _Assessing the ability of climate models to simulate the observed sensitivity of tropical cyclone intensity to sea surface temperature_, 2015
- Erik Fraza, _Spatial analyses of climatological effects on hurricane intensification rates_, 2016
- Peter Wood (co)
- Holly M. Widen, _New methods in tornado risk and vulnerability assessments_, 2016
- John M. Humphreys, _Traits, Species, and Communities: Integrative Bayesian Approaches to Ecological Biogeography across Geographic, Environmental, Phylogenetic, and Morphological Space_, 2018
- Tyler Fricker, _A Geography of Tornado Casualties in the United States_, 2019
- Gregory Burris (co), _Between proxy and instrument: Reconstructing past weather using qualitative human observations in the absence of instrumental and prox records: A case study from Shirley Plantation, Virginia_, 2021
- Zoe Schroder, _Tornado Outbreak Climatology in the United States (1995–2020): Definitions, Descriptions, and Statistical Analyses_, 2021
- Efraim Roxas (co), _Critical Vulnerability and Community Care Towards a Resilience from Below_, 2023

# MS Students Graduated

- Vincint Robert Tino, _A validation of the industrial source complex (ISC2) dispersion model in the Kuwaiti oil fire situation_, 1992 
- Jason C. Hess, _Improving seasonal predictions of hurricane activity for the Atlantic basin_, 1994
- Matthew M. Carter, _Convective rainfall regions in Puerto Rico_, 1995
- Todd B. Kimberlain, _Baroclinically-initiated hurricanes of the North Atlantic basin_, 1996
- Kwan Kong, _Landfall and post-landfall structure of Hurricane Danny and the possibility of retrieving vertical velocity profiles from rawinsonde soundings_, 1999
- David Whitehead, _An evaluation of coastal county hurricane vulnerability_, 1999
- Wei tan Pan (co), 
- Bethany Kocher, _Tropical cyclones and the North Atlantic oscillation_, 2000
- Marc D. Cooper, _The association of human activities with land degradation in the Republic of Botswana_, 2000
- Ethan J. Gibney, _An assessment of potential for economic loss to residential property in United States coastal counites [i.e., counties] from tropical cyclones using a geographical information system_, 2002
- Emily A. Fogarty, _Variations in typhoon landfalls over China_, 2004
- Jill Malmstadt, _Pre-landfall intensity as predictor of economic loss from Florida hurricanes, 1900-2007_, 2009
- Robert Edward Hodges, _Evidence for a solar influence on U.S.-affecting hurricanes_, 2009
- Ona Marie Strikas, _Modeling the spatial differentiation in cloud-to-ground lightning: A case study in Atlanta, Georgia, USA_, 2023
- Laura E. Michaels, _Spatial and temporal characteristics of the population bias in U.S. tornado reports_, 2013
- Tyler Fricker, _Estimating kinetic energy of U.S. tornadoes_, 2015
- Emily Ryan, _Florida's Tornado Climatology: Occurrence Rates, Casualties, and Property Losses_, 2018
- Zachery Taylor Law, _Wildfires in the Apalachicola National Forest, USA from 1992–2018: Relationships to Soil Dryness and Lightning_, 2022

# Grant Totals

* Risk Prediction Initiative $355,475
* National Science Foundation $1,306,348 
* National Oceanic and Atmospheric Administration $96,000
* Florida State University $122,500

# Awards

* Late Career Research Award College of Social Sciences and Public Policy, 2022, FSU.
* Earl & Sophia Shaw Endowed Chair in Geography, FSU.
* University Graduate Mentor Award, 2019, FSU.
* Gilbert F. White Distinguished Lecture Award, 2013, American Geophysical Union.
* Teaching Incentive Program Award, 1996, FSU.
* Outstanding Student Teacher Award, 1987, UWM.

# Academic Books

```{r echo=FALSE, results="asis",comment=FALSE}
file_books <- ReadBib("books.bib")
dates <- unlist(unique(file_books$year))[order(unlist(unique(file_books$year)),decreasing = TRUE)]

for (date in dates) {
  print(file_books[list(year=date)],
        .opts = list(style="markdown",bib.style ="authoryear" ,max.names = 10, dashed=FALSE)
        )
  cat("\n")
}
```

# Refereed Academic Journal Articles

```{r echo=FALSE, results="asis",comment=FALSE}
file_journals <- ReadBib("journals.bib")
dates <- unlist(unique(file_journals$year))[order(unlist(unique(file_journals$year)), decreasing = TRUE)]

for (date in dates) {
  cat(paste0("## ", date),"\n")
  print(file_journals[list(year=date)],
        .opts = list(style="markdown", bib.style ="authoryear", max.names = 10, dashed=FALSE)
        )
  cat("\n")
}
```
